\begin{resumo}[Abstract]
 \begin{otherlanguage*}{english}
  The growing number of discussions on political issues and other issues on social networks
  result in the polarization of those messages, considering the characteristics
  of the content selection algorithms used in these platforms. Therefore,
  the ``Cidade Democrática'' institute presents the idea of a new social participation
  platform, the ``Pushing Together'', to be used in web and mobile applications.
  The idea is to allow the user to create and participate of conversations, performing
  comments and/or votes on a comment of another participant. With the given votes, people
  who answered in a similar way are grouped, allowing the user to get a wide
  vision of all opinions.
  %
  The ``Pushing Together'' platform need to have these funcionalities of 
  user/conversations management and user grouping to fulfill its purpose. 
  Offering these functionalities as web services would be meaningful 
  contribution to the project. Moreover, a more flexible solution 
  would be making possible to group the users using different configurable 
  classification techniques.
  %
  The goal of this study was the implementation of a RESTful API that 
  holds all the functionalities mentioned above and an architecture
  that allows the use of different classification methods to group the users.
  %
  The study was made in five steps and the API was implemented in six iterations.
  Along with the services module (API), the architecture was proposed with another two modules,
  the client module to provide the platform graphic interface and the math module to be responsible for the user grouping.
  %
  At the end of development, an application was built to validate the API and the proposed architecture. In the validation only one math module
  was integrated. The proposed architecture and the API was considered adequate and satisfactory for the identified requirements. However, evolutions needs was
  perceived considering another functionalities for `` Pushing Together ''.
   Essentials functionalities to reduce the discussions polarization. The gap
of math modules to integrated was perceived too.
  %
  

   \vspace{\onelineskip}

   \noindent
   \textbf{Key-words}: Social participation. RESTful API. Pushing Together.
 \end{otherlanguage*}
\end{resumo}
